\section{Input/Output \& Secondary Storage}
\begin{questions}
	\subsection{Digital Cameras}
	\question Contrast a CCD and a CMOS sensor and their operation as ADCs. 
	\question Describe the working of the sensor: include transistors, pixels, RGB, file formats (e.g. RAW, TIFF), flash memory. 
	\question What is meant by pixellation? 
	\question Define resolution. 
	\question ``More megapixels are better''. Discuss.  
	\subsection{RFID Readers}
	\question What is the difference between active and passive RFids?
	\question Suggest some uses for RFid tags. What are typical ranges for an RFid tag?  
	\subsection{Laser Printers}
	\question Describe how a laser printer works. 
	\question Why do we discuss printing in terms of CMYK rather than RGB?
	\question True or false? ``Laser printers do not use ink.'' Defend your assertion. 
	\subsection{Barcode Scanners}
	\subsection{Magnetic, Solid State \& Optical Disks}
	\question Contrast a magnetic hard drive's method of operation with an SSD. 
	\question Pick a suitable secondary storage medium --- or other methodology if more appropriate --- for the following tasks, outlining reasons for your choice, also suggest approximate sizes for each task: 
	\begin{parts}
		\part Transferring a 90 minute 4K video file from a laptop at home to a school machine;
		\part Backing up your project documentation, as either MS Word or \LaTeX; 
		\part Sending a short (e.g. less than an hour) audio file to a colleague;
		\part Working medium term storage for a laptop computer at a remote research site; 
		\part Backing up the work from that same laptop.   		
	\end{parts}
	\question What is the limiting factor on the storage of an SSD? 
	\question Within the context of storage define: 
	\begin{parts}
		\part Latency
		\part Fragmentation 
		\part Block
		\part Sector 
	\end{parts}
\end{questions}